\vspace{-2.5cm}A generative model for urban firm networks

### 2020-09-24 communications/NetSci2020/slidesNetSci.tex
Update on Overleaf.

\title
[A generative model for urban firm networks]{A generative model for urban firm networks}
\author[Raimbault \and Zdanowska]{J.~Raimbault$^{1,2,3\ast}$ \and N. Zdanowska$^{1,3}$\\\medskip
$^{\ast}$\texttt{n.zdanowska@ucl.ac.uk}
}

@@

 \begin{center}
 \includegraphics[width=0.7\textwidth]{figures/Fig2.png}
 \end{center}

@@

 \begin{center}
 \includegraphics[width=0.67\textwidth]{figures/Fig3.png}
 \end{center}

@@

\sframe{Effect of sector proximity}{

@@

     \includegraphics[width=0.48\textwidth]{../../figuresraw/internationalisation-gammaSectors_errorbars.png}
    \includegraphics[width=0.48\textwidth]{../../figuresraw/metropolisation-gammaSectors_errorbars.png}

    \medskip
    \footnotesize

    \textit{(Left) Internationalization varies linearly with sector proximity $\gamma_S$; (Right) Correlation between degree and size exhibits a maximum, witnessing an intermediate regime where size is the most important}

\sframe{Grid exploration: internationalization}{

    \begin{center}
    \includegraphics[width=\textwidth]{../../figures/Fig5.png}
    \end{center}

    \textit{The transition as a function of interaction range depends on the influence of origin size $\gamma_F$; sector proximity $\gamma_S$ plays a role only for a large influence of the origin.}

@@

    \begin{center}
    	\includegraphics[height=0.75\textheight]{figures/Fig8.png}

@@

    \begin{center}
    	\includegraphics[height=0.72\textheight]{figures/Fig9.png}

>>>>

\title
[A generative model for urban firm networks]{A generative model for urban firm networks}
\author[Raimbault \and Zdanowska \and Arcaute] {J.~Raimbault$^{1,2,3}$ \and N. Zdanowska$^{1,3}\ast$ \and E. Arcaute$^{1}$\\\medskip
$^{\ast}$\texttt{n.zdanowska@ucl.ac.uk}
}

@@

 \begin{center}
 \includegraphics[width=0.7\textwidth]{../../figures/Fig2.png}
 \end{center}

@@

 \begin{center}
 \includegraphics[width=0.67\textwidth]{../../figures/Fig3.png}
 \end{center}

@@

% \sframe{Effect of sector proximity}{

@@

     % \includegraphics[width=0.48\textwidth]{../../figuresraw/internationalisation-gammaSectors_errorbars.png}
    % \includegraphics[width=0.48\textwidth]{../../figuresraw/metropolisation-gammaSectors_errorbars.png}

    % \medskip
    % \footnotesize

    % \textit{(Left) Internationalization varies linearly with sector proximity $\gamma_S$; (Right) Correlation between degree and size exhibits a maximum, witnessing an intermediate regime where size is the most important}

% }

% \sframe{Grid exploration: internationalization}{

    % \begin{center}
    % \includegraphics[width=\textwidth]{../../figures/Fig5.png}
    % \end{center}

    % \medskip

    % \footnotesize

    % \textit{The transition as a function of interaction range % % depends on the influence of origin size $\gamma_F$; sector % proximity $\gamma_S$ plays a role only for a large influence of the origin.}

% }

@@

    \begin{center}
    	\includegraphics[height=0.75\textheight]{../../figures/Fig8.png}

@@

    \begin{center}
    	\includegraphics[height=0.72\textheight]{../../figures/Fig9.png}
